Sampling requirements to detect ecosystem change

### 2020-03-06 R/manuscript_draft.Rmd
correct x label of Fig 2 (it said phi instead of sigma)

p1 <- 
ggplot(simulation_all %>% filter(Parameter == unique(simulation_all$Parameter)[1]), aes(Param, min_time)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept=ar_vr$acf[2], lty=2) + 
  facet_wrap(~Parameter, scales="free_x", 
             labeller = label_glue('a. {Parameter}')) +
  ylim(20,50) +
  labs(x=c("phi"), y= "Minimum number of samples required") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        strip.background = element_rect(colour="transparent", fill="transparent"),
        strip.text.x = element_text(angle = 0, hjust = 0))
p2 <- ggplot(simulation_all %>% filter(Parameter == unique(simulation_all$Parameter)[2]), aes(Param, min_time)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = sd_vr, lty=2) +
  facet_wrap(~Parameter, scales="free_x", 
             labeller = label_glue('b. {Parameter}')) +
  ylim(20,50) +
  labs(x="phi", y= "") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        strip.background = element_rect(colour="transparent", fill="transparent"),
        strip.text.x = element_text(angle = 0, hjust = 0))
p3 <- ggplot(simulation_all %>% filter(Parameter == unique(simulation_all$Parameter)[3]), aes(Param, min_time))  +
  geom_point() +
  geom_line() + 
  geom_vline(xintercept = shift_vr, lty=2) +
  facet_wrap(~Parameter, scales="free_x", 
             labeller = label_glue('c. {Parameter}')) +
  ylim(20,50) +
  labs(x="shift size", y= "") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        strip.background = element_rect(colour="transparent", fill="transparent"),
        strip.text.x = element_text(angle = 0, hjust = 0))

>>>>

p1 <- 
ggplot(simulation_all %>% filter(Parameter == unique(simulation_all$Parameter)[1]), aes(Param, min_time)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept=ar_vr$acf[2], lty=2) + 
  facet_wrap(~Parameter, scales="free_x", 
             labeller = label_glue('a. {Parameter}')) +
  ylim(20,50) +
  labs(x=c("sigma"), y= "Minimum number of samples required") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        strip.background = element_rect(colour="transparent", fill="transparent"),
        strip.text.x = element_text(angle = 0, hjust = 0))
p2 <- ggplot(simulation_all %>% filter(Parameter == unique(simulation_all$Parameter)[2]), aes(Param, min_time)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = sd_vr, lty=2) +
  facet_wrap(~Parameter, scales="free_x", 
             labeller = label_glue('b. {Parameter}')) +
  ylim(20,50) +
  labs(x="phi", y= "") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        strip.background = element_rect(colour="transparent", fill="transparent"),
        strip.text.x = element_text(angle = 0, hjust = 0))
p3 <- ggplot(simulation_all %>% filter(Parameter == unique(simulation_all$Parameter)[3]), aes(Param, min_time))  +
  geom_point() +
  geom_line() + 
  geom_vline(xintercept = shift_vr, lty=2) +
  facet_wrap(~Parameter, scales="free_x", 
             labeller = label_glue('c. {Parameter}')) +
  ylim(20,50) +
  labs(x="shift size", y= "") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        strip.background = element_rect(colour="transparent", fill="transparent"),
        strip.text.x = element_text(angle = 0, hjust = 0))
